Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
+

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_}   \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \mathsf{nextpaddr} \in \Xi\setminus \{ \mathsf{entry} \} \} }_{\rtv}$

@@

>>>>

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{_} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_}   \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \mathsf{nextpaddr} \in \Xi\setminus \{ \mathsf{entry} \}) }_{\rtv}$

@@

$\specline{\ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
